Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-15 figures/fig-cc_edge_fn_example.tex
applying comments

\begin{figure}%
  \centering
    \tikzstyle{supergraph}=[
      fill=greyblue,
      rounded corners,
      font=\footnotesize,
      align=right,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_y}=[
      fill=bisque,
      rounded corners,
      font=\footnotesize,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_f}=[
      fill=lightsalmonpink,
      rounded corners,
      font=\footnotesize,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{description}=[fill=white]
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
    \tikzstyle{arrowtext}=[font=\tiny,color=black,above]

@@

    \node [n,label=$\Lambda$] (st_main_z) [right=\nd of st_main.east] {};
    \node [n,label=\texttt{v}] (st_main_v) [right=\nd of st_main_z] {};
    \node [n] (asgn_a_z) [right=\nd of asgn_a.east] {};
    \node [n] (call_foo_z) [right=\nd of call_foo.east] {};
    \node [n] (return_foo_z) [right=\nd of return_foo.east] {};
    \node [n] (call_bar_z) [right=\nd of call_bar.east] {};
    \node [n] (return_bar_z) [right=\nd of return_bar.east] {};
    \node [n] (end_main_z) [right=\nd of end_main.east] {};
    \node [n] (asgn_a_v) [right=\nd of asgn_a_z] {};
    \node [n] (call_foo_v) [right=\nd of call_foo_z] {};
    \node [n] (return_foo_v) [right=\nd of return_foo_z] {};
    \node [n] (call_bar_v) [right=\nd of call_bar_z] {};
    \node [n] (return_bar_v) [right=\nd of return_bar_z] {};
    \node [n] (end_main_v) [right=\nd of end_main_z] {};
% main method edges
    \path[->](st_main_z) edge (asgn_a_z);
    \path[->](asgn_a_z) edge (call_foo_z);
    \path[->](call_foo_z) edge (return_foo_z);
    \path[->](return_foo_z) edge (call_bar_z);
    \path[->](call_bar_z) edge (return_bar_z);
    \path[->](return_bar_z) edge (end_main_z);  
    \path[->](st_main_v) edge (asgn_a_v);
    \path[->](asgn_a_v) edge (call_foo_v);
    \path[->](call_foo_v) edge (return_foo_v);
    \path[->](return_foo_v) edge (call_bar_v);
    \path[->](call_bar_v) edge (return_bar_v);
    \path[->](return_bar_v) edge (end_main_v);

@@

    \node [n,label=$\psi$] (st_a_foo_p) [left=\nd of st_a_foo.west] {};
    \node [n] (return_secret_p) [left=\nd of return_secret.west] {};
    \node [n] (end_a_foo_p) [left=\nd of end_a_foo.west] {};
    \node [n,label=$\Lambda$] (st_a_foo_z) [left=\nd of st_a_foo_p] {};
    \node [n] (return_secret_z) [left=\nd of return_secret_p] {};
    \node [n] (end_a_foo_z) [left=\nd of end_a_foo_p] {};
%A.foo method edges
    \path[->](st_a_foo_z) edge (return_secret_z); 
    \path[->](return_secret_z) edge node[arrowtext,near start,above right=0.4cm and -.15cm,rotate=-60]{$\lambda m.\botcc$} (end_a_foo_z); 
    \path[->,dashed](call_foo_z) edge [out=38,in=238]  (st_a_foo_z);
    \path[->,dashed](end_a_foo_z) edge [out=200,in=43] (return_foo_z);
    \path[->,dashed](end_a_foo_p) edge  [out=200,in=43] node[arrowtext,below,rotate=30]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (return_foo_v);
    \path[->](st_a_foo_p) edge (return_secret_p); 
    \path[->](return_secret_p) edge (end_a_foo_p);
    \path[->](return_secret_z) edge (end_a_foo_p);

@@

    \node [n,label=\texttt{s}] (st_a_bar_s) [left=\nd of st_a_bar.west] {};
    \node [n,label=$\Lambda$] (st_a_bar_z) [left=\nd of st_a_bar_s] {};
    \node [n] (end_a_bar_s) [left=\nd of end_a_bar.west] {};    
    \node [n] (end_a_bar_z) [left=\nd of end_a_bar_s] {};
%A.bar method edges
    \path[->](st_a_bar_z) edge (end_a_bar_z);
    \path[->,dashed](call_bar_z) edge [out=20,in=229] (st_a_bar_z);
    \path[->,dashed](end_a_bar_z) edge [out=220,in=35] (return_bar_z);
    \path[->](st_a_bar_s) edge (end_a_bar_s);
    \path[->,dashed](call_bar_v) edge [out=20,in=230] node[arrowtext,near end,above left=-.1cm and -.15cm,rotate=36]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (st_a_bar_s);

@@

    \node [n,label=$\Lambda$] (st_b_foo_z) [left=\nd of st_b_foo.west] {};
    \node [n] (return_not_secret_z) [left=\nd of return_not_secret.west] {};
    \node [n] (end_b_foo_z) [left=\nd of end_b_foo.west] {};

@@

    \node [n,label=\texttt{s}] (st_b_bar_s) [left=\nd of st_b_bar.west] {};
    \node [n] (print_s) [left=\nd of print.west] {};
    \node [n] (end_b_bar_s) [left=\nd of end_b_bar.west] {};
    \node [n,label=$\Lambda$] (st_b_bar_z) [left=\nd of st_b_bar_s] {};
    \node [n] (print_z) [left=\nd of print_s] {};
    \node [n] (end_b_bar_z) [left=\nd of end_b_bar_s] {};
%B.bar method edges
    \path[->](st_b_bar_z) edge (print_z);
    \path[->](print_z) edge (end_b_bar_z);
    \path[->](st_b_bar_s) edge (print_s);
    \path[->](print_s) edge (end_b_bar_s);
    \path[->,dashed](call_bar_z) edge [out=40,in=140,color=lightsalmonpink] (st_b_bar_z);
    \path[->,dashed](call_bar_v) edge [out=20,in=160,color=lightsalmonpink] node[arrowtext,above right=-.4cm and .4cm,rotate=-10]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$} (st_b_bar_s);
    \path[->,dashed](end_b_bar_z) edge [out=210,in=-40,color=lightsalmonpink] (return_bar_z);    
}
\end{tikzpicture}
\caption[An example program demonstrating correlated-call edge functions on the $\Lambda$-node path for Listing~\ref{list:ccexample}]{An example program demonstrating correlated-call edge functions on the $\Lambda$-node path for Listing~\ref{list:ccexample}. All non-labeled edges are implicitly labeled with identity functions $\id$. The variable corresponding to an initial secret value is denoted as $\psi$.}%
  \label{fig:cc_edgefn_example}%  
  \end{figure}

>>>>

\begin{figure}[h!]%
  \centering
    \tikzstyle{supergraph}=[
      fill=greyblue,
      rounded corners,
      font=\footnotesize,
      align=right,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_y}=[
      fill=bisque,
      rounded corners,
      font=\footnotesize,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{supergraph_f}=[
      fill=lightsalmonpink,
      rounded corners,
      font=\footnotesize,
      align=left,
      text=charcoal,
      drop shadow={ashadow, color=greyblue}
    ]
    \tikzstyle{description}=[fill=white]
    \tikzstyle{n}=[fill=black,circle,inner sep=1.5pt]
    \tikzstyle{arrowtext}=[font=\tiny,color=black,above]

@@

    \node [n,label=$\mathbf0$] (st_main_z) [right=\nd of st_main.east] {};
    \node [n,label=\texttt{v}] (st_main_v) [right=\nd of st_main_z] {};
    \node [n] (asgn_a_z) [right=\nd of asgn_a.east] {};
    \node [n] (call_foo_z) [right=\nd of call_foo.east] {};
    \node [n] (return_foo_z) [right=\nd of return_foo.east] {};
    \node [n] (call_bar_z) [right=\nd of call_bar.east] {};
    \node [n] (return_bar_z) [right=\nd of return_bar.east] {};
    \node [n] (end_main_z) [right=\nd of end_main.east] {};
    \node [n] (asgn_a_v) [right=\nd of asgn_a_z] {};
    \node [n] (call_foo_v) [right=\nd of call_foo_z] {};
    \node [n] (return_foo_v) [right=\nd of return_foo_z] {};
    \node [n] (call_bar_v) [right=\nd of call_bar_z] {};
    \node [n] (return_bar_v) [right=\nd of return_bar_z] {};
    \node [n] (end_main_v) [right=\nd of end_main_z] {};
% main method edges
    \path[->](st_main_z) edge (asgn_a_z);
    \path[->](asgn_a_z) edge (call_foo_z);
    \path[->](call_foo_z) edge (return_foo_z);
    \path[->](return_foo_z) edge (call_bar_z);
    \path[->](call_bar_z) edge (return_bar_z);
    \path[->](return_bar_z) edge (end_main_z);  
    \path[->](st_main_v) edge (asgn_a_v);
    \path[->](asgn_a_v) edge (call_foo_v);
    \path[->](call_foo_v) edge (return_foo_v);
    \path[->](return_foo_v) edge (call_bar_v);
    \path[->](call_bar_v) edge (return_bar_v);
    \path[->](return_bar_v) edge (end_main_v);

@@

    \node [n,label=$r$] (st_a_foo_p) [left=\nd of st_a_foo.west] {};
    \node [n] (return_secret_p) [left=\nd of return_secret.west] {};
    \node [n] (end_a_foo_p) [left=\nd of end_a_foo.west] {};
    \node [n,label=$\mathbf0$] (st_a_foo_z) [left=\nd of st_a_foo_p] {};
    \node [n] (return_secret_z) [left=\nd of return_secret_p] {};
    \node [n] (end_a_foo_z) [left=\nd of end_a_foo_p] {};
%A.foo method edges
    \path[->](st_a_foo_z) edge (return_secret_z); 
    \path[->](return_secret_z) edge node[arrowtext,near start,above right=0.4cm and -.15cm,rotate=-60]{$\lambda m.\botcc$} (end_a_foo_z); 
    \path[->,dashed](call_foo_z) edge [out=38,in=238]  (st_a_foo_z);
    \path[->,dashed](end_a_foo_z) edge [out=200,in=43] (return_foo_z);
    \path[->,dashed](end_a_foo_p) edge  [out=200,in=43] node[arrowtext,below,rotate=30]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (return_foo_v);
    \path[->](st_a_foo_p) edge (return_secret_p); 
    \path[->](return_secret_p) edge (end_a_foo_p);
    \path[->](return_secret_z) edge (end_a_foo_p);

@@

    \node [n,label=\texttt{s}] (st_a_bar_s) [left=\nd of st_a_bar.west] {};
    \node [n,label=$\mathbf0$] (st_a_bar_z) [left=\nd of st_a_bar_s] {};
    \node [n] (end_a_bar_s) [left=\nd of end_a_bar.west] {};    
    \node [n] (end_a_bar_z) [left=\nd of end_a_bar_s] {};
%A.bar method edges
    \path[->](st_a_bar_z) edge (end_a_bar_z);
    \path[->,dashed](call_bar_z) edge [out=20,in=229] (st_a_bar_z);
    \path[->,dashed](end_a_bar_z) edge [out=220,in=35] (return_bar_z);
    \path[->](st_a_bar_s) edge (end_a_bar_s);
    \path[->,dashed](call_bar_v) edge [out=20,in=230] node[arrowtext,near end,above left=-.1cm and -.15cm,rotate=36]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$} (st_a_bar_s);

@@

    \node [n,label=$\mathbf0$] (st_b_foo_z) [left=\nd of st_b_foo.west] {};
    \node [n] (return_not_secret_z) [left=\nd of return_not_secret.west] {};
    \node [n] (end_b_foo_z) [left=\nd of end_b_foo.west] {};

@@

    \node [n,label=\texttt{s}] (st_b_bar_s) [left=\nd of st_b_bar.west] {};
    \node [n] (print_s) [left=\nd of print.west] {};
    \node [n] (end_b_bar_s) [left=\nd of end_b_bar.west] {};
    \node [n,label=$\mathbf0$] (st_b_bar_z) [left=\nd of st_b_bar_s] {};
    \node [n] (print_z) [left=\nd of print_s] {};
    \node [n] (end_b_bar_z) [left=\nd of end_b_bar_s] {};
%B.bar method edges
    \path[->](st_b_bar_z) edge (print_z);
    \path[->](print_z) edge (end_b_bar_z);
    \path[->](st_b_bar_s) edge (print_s);
    \path[->](print_s) edge (end_b_bar_s);
    \path[->,dashed](call_bar_z) edge [out=40,in=140,color=lightsalmonpink] (st_b_bar_z);
    \path[->,dashed](call_bar_v) edge [out=20,in=160,color=lightsalmonpink] node[arrowtext,above right=-.4cm and .4cm,rotate=-10]{$\lambda m.m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$} (st_b_bar_s);
    \path[->,dashed](end_b_bar_z) edge [out=210,in=-40,color=lightsalmonpink] (return_bar_z);    
}
\end{tikzpicture}
\caption[An example program demonstrating correlated-call edge functions on the $\mathbf0$-node path for Listing~\ref{list:ccexample}]{An example program demonstrating correlated-call edge functions on the $\mathbf0$-node path for Listing~\ref{list:ccexample}. All non-labeled edges are implicitly labeled with identity functions $\id$. The variable $\psi$ denotes the return value of the \texttt{A.foo} method.}%
  \label{fig:cc_edgefn_example}%  
  \end{figure}
